% Document Type: LaTeX
% Master File: tests.tex
\documentclass{article}
\usepackage{a4}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage{epic,eepic}
\usepackage{amssymb}

\newcommand{\run}{{\mathbb R}}
\newcommand{\nun}{{\mathbb N}}
\newcommand{\bral}{\left<}
\newcommand{\brar}{\right>}
\newcommand{\Th}[1]{\mathcal{T}^{h}_{#1}}
\newcommand{\Sh}[1]{\mathcal{S}^{h}_{#1}}
\newcommand{\Nui}[1]{{\mathcal N}_{#1}}
\newcommand{\ovl}{\overline}
\newcommand{\dps}{\displaystyle}
\newcommand{\Hdiv}[1]{{\cal H}(\mbox{div},#1)}
\newcommand{\p}{\partial}
\newcommand{\nab}{\mbox{\boldmath $\nabla$}}
\newcommand{\ocamlpiiil}{{\sf OcamlP3l}}
\newcommand{\ocaml}{{\sf Ocaml}}
\newcommand{\pppl}{{\sf p3l}}

\title{Coupling numerical codes using the \ocamlpiiil\ functional parallel programming system
       \thanks{The OcamlP3l system has been partially funded by a Galileo bilateral France-Italy project. }}
\author{Fran\c{c}ois Cl\'ement, Roberto Di Cosmo, Vincent Martin, Pierre Weis, Arnaud Vodicka}

\begin{document}
\maketitle

\begin{abstract}
  Writing parallel programs is not easy, and debugging them is usually
  a nightmare.  To cope with these difficulties, a structured approach
  to parallel programs using skeletons and template based compiler
  techniques has been developed over the past years by several
  researchers, including the P3L group in Pisa. The \ocamlpiiil\ 
  system marries the Ocaml functional programming language with the
  P3L skeletons, yielding a powerful parallel programming environment,
  that has evolved over the years.

  In this paper, we report on the successful application of the \ocamlpiiil\
  in the field of scientific computing, where the system has been used to 
  solve the problem of coupling numerical codes, obtaining parallelization
  for free.

  The interaction has been extremely fruitful, as, in the process of solving the
  coupling problem, a wealth of new ideas have emerged on the design of the
  system, which are incorporated in the current version of  \ocamlpiiil.

\end{abstract}

\section{Introduction and Overview}

\include{introduction}

%
% partie \ocamlpiiil
%
\include{caml}

%
% partie numerique
%
\include{estime}

% in conclusions\ldots{}
% stream manipulation inside user functions

\bibliographystyle{alpha}

\bibliography{jfp}
% *****EXPORTBEGS: \bibliography{main.bbl}
\newcommand{\etalchar}[1]{$^{#1}$}
\begin{thebibliography}{DDCLP98}

\bibitem[Col89]{cole-th}
M.~Cole.
\newblock {\em {Algorithmic Skeletons: Structured Management of Parallel
  Computations}}.
\newblock Research Monographs in Parallel and Distributed Computing. Pitman,
  1989.

\bibitem[DDCLP98]{Ocamlp3lMlw98}
Marco Danelutto, Roberto Di~Cosmo, Xavier Leroy, and Susanna Pelagatti.
\newblock Parallel functional programming with skeletons: the ocamlp3l
  experiment.
\newblock {\em The ML Workshop}, 1998.

\bibitem[DFH{\etalchar{+}}93]{ic-parle-93-1}
J.~Darlington, A.~J. Field, P.~G. Harrison, P.~H.~J. Kelly, D.~W.~N. Sharp, and
  Q.~Wu.
\newblock {Parallel Programming Using Skeleton Functions}.
\newblock In {\em PARLE'93}, pages 146--160. Springer, 1993.
\newblock LNCS No. 694.

\bibitem[DGTY95]{darli-to-1}
J.~Darlington, Y.~Guo, H.~W. To, and J.~Yang.
\newblock {Parallel Skeletons for Structured Composition}.
\newblock In {\em Fifth ACM SIGPLAN Symposium on Principles and Practice of
  Parallel Programming}. ACM Press, July 1995.

\bibitem[DMO{\etalchar{+}}92]{fgcs-firenze}
M.~Danelutto, R.~Di Meglio, S.~Orlando, S.~Pelagatti, and M.~Vanneschi.
\newblock A methodology for the development and support of massively parallel
  programs.
\newblock {\em Future Generation Computer Systems}, 8(1--3):205--220, July
  1992.

\end{thebibliography}
